---
title: "Pre-processing - Variable Scaling"
output: html_document
---

```{r, include=FALSE}

knitr::opts_chunk$set(fig.width = 16, fig.height = 12)
options(width = 100)

source("~/MCD/m.R")

print("Loaded")
```


Useful to improve the numeric stability of some calculations,

Main downside is a loss of interpretability of individual values.

## Scale

The scale transform calculates the standard deviation for an attribute and divides each 
value by that standard deviation. 

Scaling the data coerce the values to have a common standard deviation of one.

This is a useful operation for scaling data with a Gaussian distribution consistently.

```{r}
m_input_data(iris) %>% m_response(~Species) %>% m_scale_transform() %>% m_variable_statistics() %>% m_query(~ variable_statistics)
```

## Center Data

The center transform calculates the mean for an attribute and subtracts it from each value.

As a result of centering the predictor has a zero mean.

```{r}
m_input_data(iris) %>% m_response(~Species) %>% m_center_transform() %>% m_variable_statistics() %>% m_query(~variable_statistics)
```

## Standardize Data

Combining the scale and center transforms will standardize your data. 
Attributes will have a mean value of 0 and a standard deviation of 1.

```{r}
m_input_data(iris) %>% m_response(~Species) %>% m_standardize_transform() %>% m_variable_statistics() %>% m_query(~variable_statistics)
```

## Normalize Data

Data values can be scaled into the range of [0, 1] which is called normalization.

```{r}
m_input_data(iris) %>% m_response(~Species) %>% m_range_transform() %>% m_variable_statistics() %>% m_query(~variable_statistics)
```
