---
title: "Pre-processing - Resolve Skewness"
output: html_document
---

```{r, include = FALSE}

knitr::opts_chunk$set(fig.width = 16, fig.height = 12)
options(width = 100)

source("~/MCD/m.R")

library(mlbench)
data(PimaIndiansDiabetes)

print("Loaded")
```

## Tips

+ Right-skewed distribution has a large number of data points on the left-side of the distribution. Or another way, there 
is a greater number of data points at relatively small values.

+ Data whose ratio of the highest to lower greater than 20 has significant skew.

+ Skewness statistic can be a diagnostic. Zero is symmetric, greater zero is right-skewed, less-zero is left-skewed.

+ Replacing the data with log, square-root or inverse may help to remove skew.

## Skewed Statistics

When an attribute has a Gaussian-like distribution but is shifted, this is called a skew. 

```{r Base}

# summarize pedigree and age
m_input_data(PimaIndiansDiabetes[, 7:8]) %>% m_variable_statistics() %>% m_query(~ variable_statistics)

m_density(PimaIndiansDiabetes[, 7:8]) %>% m_layout()

```

## Box-Cox Transform

The distribution of an attribute can be shifted to reduce the skew and make it more 
Gaussian. The BoxCox transform can perform this operation (assumes all values are positive).


```{r}

boxcox_m <- m_input_data(PimaIndiansDiabetes[, 7:8]) %>% m_boxcox_transform() %>% m_pre_processed_data() %>% m_variable_statistics() %>% m_run()
boxcox_m$variable_statistics
boxcox_m %>% m_density() %>% m_layout()

```

## 9.8 Yeo-Johnson Transform

The YeoJohnson transform another power-transform like Box-Cox, but it supports raw values that are 
equal to zero and negative.

```{r}
yeo_m <- m_input_data(PimaIndiansDiabetes[, 7:8]) %>% m_yeojohnson_transform() %>% m_pre_processed_data() %>% m_variable_statistics() %>% m_run()
yeo_m$variable_statistics
yeo_m %>% m_density() %>% m_layout()

```
