---
title: "Model Evaluation - Tuning"
output: html_document
---

# Notes

+ Many models have important parameters which cannot be directly estimated from the data.

+ Poor choices for these parameters can result in over-fitting.

## Approaches for tuning

A general approach is to define a set of candiate values, generate reliable estimates of 
model utility across the candidate values, then choose the optimal settings.

Another approach is genetic algorithms. (APM - Mitchel 1998)

Another approach is simplex search methods. (APM - Olsson and Nelson 1975)

# Computation

Taken from APM Chapter 4. Load data.

```{r}

source("~/MCD/MCD/m.R")

library(caret)
data(GermanCredit)

GermanCredit <- GermanCredit[, - caret::nearZeroVar(GermanCredit)]
GermanCredit$CheckingAccountStatus.lt.0 <- NULL
GermanCredit$SavingsAccountBonds.lt.100 <- NULL
GermanCredit$EmploymentDuration.lt.1 <- NULL
GermanCredit$EmploymentDuration.Unemployed <- NULL
GermanCredit$Personal.Male.Married.Widowed <- NULL
GermanCredit$Property.Unknown <- NULL
GermanCredit$Housing.ForFree <- NULL

gc_p <- m_data(GermanCredit) %>% m_response("Class") %>% m_stratified_split(p = 0.8) %>% m_seed(1056)

print("Data Loaded")

```

## Tune length

Set the tune length. A set of tuing parameters was automatically selected.

```{r}

gc_tune_m <- gc_p %>%
    m_accuracy_metric() %>%
    m_standardize_transform() %>%
    m_cross_validation() %>%
    m_support_vector_machine_radial_basis(tune_length = 10) %>%
    m_train()

gc_tune_m %>% m_get_results_data() %>% m_linechart(x = ~C, y = ~Accuracy, sd = ~AccuracySD, plot = ~base_plot + scale_x_log10())


```
